%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Philippe Remy} % Your name
\address{Ebisu, 1 Chome 10-7 apt 901, 150-0021, Tokyo, Japan} % Your address
\address{https://github.com/philipperemy \\ https://philipperemy.github.io/}
\address{(+81) 80 4916 9112 \\ premy@cogent.co.jp} % Your phone number and email


\begin{document}

\begin{rSection}{Profile}
Researcher Engineer in deep learning with an extensive experience designing and
implementing innovative methods to solve complex mathematical and computational problems.
Former software developer working for Front Office businesses in investment banking.
My objective is to conceive and implement simple software solutions to complex mathematical and algorithmic problems.

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Imperial College, London} \hfill {\em 2014-2015} \\ 
MSc in Statistics, Distinction \\
Best MSc thesis of the year (awarded Winton Capital Prize) \\
Finalist of the Warner Prize \\

{\bf Ecole Nationale Superieure d'Informatique et Mathematiques, Bordeaux} \hfill {\em 2009-2012} \\ 
Meng in Computer Science \& Engineering, First Class Honours \\
French Leading Grande Ecole \\

{\bf Institut Polytechnique, Bordeaux} \hfill {\em 2007-2009} \\ 
Renowned intensive program in Mathematics \& Physics, First Class Honours \\


\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{COGENT LABS}{November 2015 - Present}{Research Engineer}{Tokyo, Japan}
\item Convolutional Neural Networks
\item Long Short Memory Networks
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Imperial College (supervised by HSBC)}{April 2015 - September 2015}{Graduate Researcher}{London, UK}
\item This project investigates the practical benefit of using more complex modeling than what is currently standard practice in applications related to statistical arbitrage. The underlying assets will be modeled using appropriate mean-reverting time series or state space models. In order to fit these models to real data the project will involve using advanced particle methods such as Particle Markov Chain Monte Carlo.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Societe Generale}{August 2012 - September 2014}{Low Latency Market Access Software Developer}{Paris, France}
\item Vivamus PostgreSQL fermentum semper porta. Nunc diam velit PHP, adipiscing ut tristique vitae
\item Maecenas convallis ullamcorper ultricies stylesheets.
\end{rSubsection}

\begin{rSubsection}{BNP Paribas}{August 2012 - September 2014}{Software Engineer}{Paris, France}
\item Vivamus PostgreSQL fermentum semper porta. Nunc diam velit PHP, adipiscing ut tristique vitae
\item Maecenas convallis ullamcorper ultricies stylesheets.
\end{rSubsection}

\begin{rSubsection}{Pohang University of Technology}{August 2012 - September 2014}{Data Mining Student}{Paris, France}
\item Vivamus PostgreSQL fermentum semper porta. Nunc diam velit PHP, adipiscing ut tristique vitae
\item Maecenas convallis ullamcorper ultricies stylesheets.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Mathematics & Bayesian Statistics, Operational Research, Computer Vision, \\ 
 & Deep Learning, Machine Learning, Particle Markov Chain Monte \\
 & Carlo, Applied Mathematics, Mathematical Finance \\
Computer Languages & Python, R, MATLAB, Java, C/C++, Lua, SQL \\
Deep Learning Frameworks & Tensorflow, Keras, Torch
\end{tabular}

\end{rSection}

\begin{rSection}{Languages (ILR Scale)}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
French & Native \\ 
English & Full professional proficiency \\
Spanish & Professional working proficiency \\
Japanese & Casual conversational proficiency
\end{tabular}

\end{rSection}

\begin{rSection}{Interests}
- Applying deep learning to large scale datasets \\
- Open source projects (Tensorflow implementation of Phased LSTM, attention module for Keras, multiple object detector on 9000 classes, wrapper for Stanford NLP Open IE, Deep Speaker, Keras module to visualize layers...) \\ 
- Living, traveling and discovering around the world \\
- Hacking
\end{rSection}

\begin{rSection}{Commitments}

2017. Author of the course Advanced Deep Learning with Keras, produced with Packt Publishing.

2010-2012. Co-Founder and Lecturer at Club Finance Bordeaux. Gave talks on topics related to finance, mathematics and computer science. (Club Finance Bordeaux is a student association located on the university campus).

2012-2014. Former member of MakeSense, an open project focused on social entrepreneurship and social business started in Paris on February 2010. MakeSense has a strong worldwide community of more than 10,000 members which are organizing brainstorming events in the world’s largest cities to help entrepreneurs take up their challenges.


\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
